Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-12 content/example.tex
highlight and font

In the case of our example, the control flow within each of the methods is straightforward and
all interesting issues arise from interprocedural control flow. In particular,
note that, since the variable \code{a} may point to either an \code{A}-object or a \code{B}-object, 
the call on line~\ref{line:callfoo} may dispatch to either \code{A.foo()} or to \code{B.foo()},
and this is reflected by edges  
  from the node labeled $\code{call}_\code{foo}$ to the nodes labeled
  $\code{Start}_\code{A.foo()}$ and $\code{Start}_\code{B.foo()}$
and by edges
  from the nodes labeled $\code{End}_\code{A.foo}$ and $\code{End}_\code{B.foo}$ 
  to the node labeled  $\code{return}_\code{foo}$.  
Similarly, there are edges from the node labeled $\code{call}_\code{bar}$ to the nodes 
$\code{Start}_\code{A.bar()}$ and $\code{Start}_\code{B.bar()}$, and 
edges
  from the nodes labeled $\code{End}_\code{A.bar}$ and $\code{End}_\code{B.bar}$ 
  to the node labeled  $\code{return}_\code{bar}$.

@@

The main contribution of this paper is an algorithm for transforming an IFDS problem 
into an IDE problem that expresses the feasibility of paths
in light of correlated calls.
Informally speaking, our approach associates with each edge in an
interprocedural control flow graph a function that records the types of 
variables that are used as the receiver of correlated method calls. Paths that 
are composed of edges in which the same receiver expression has different types
are infeasible, and the propagation of dataflow facts along such paths is
prevented. Applying our technique to an IFDS-based taint analysis would enable
the resulting IDE-based taint analysis to determine that no secret value can flow from
line~\ref{line:Afoo} to the print statement on line~\ref{line:Bbar}.

>>>>

In the case of our example, the control flow within each of the methods is straightforward and
all interesting issues arise from interprocedural control flow. In particular,
note that, since the variable \code{a} may point to either an \code{A}-object or a \code{B}-object, 
the call on line~\ref{line:callfoo} may dispatch to either \code{A.foo()} or to \code{B.foo()},
and this is reflected by edges  
  from the node labeled $\highlight{\code{call}_\code{foo}}{greyblue}$ to the nodes labeled
  $\highlight{\code{start}_\code{A.foo()}}{bisque}$ and $\highlight{\code{start}_\code{B.foo()}}{lightsalmonpink}$
and by edges
  from the nodes labeled $\highlight{\code{end}_\code{A.foo}}{bisque}$ and $\highlight{\code{end}_\code{B.foo}}{lightsalmonpink}$ 
  to the node labeled  $\highlight{\code{return}_\code{foo}}{greyblue}$.  
Similarly, there are edges from the node labeled $\highlight{\code{call}_\code{bar}}{greyblue}$ to the nodes 
$\highlight{\code{start}_\code{A.bar()}}{bisque}$ and $\highlight{\code{start}_\code{B.bar()}}{lightsalmonpink}$, and 
edges
  from the nodes labeled $\highlight{\code{end}_\code{A.bar}}{bisque}$ and $\highlight{\code{end}_\code{B.bar}}{lightsalmonpink}$ 
  to the node labeled  $\highlight{\code{return}_\code{bar}}{greyblue}$.

@@

The main contribution of this paper is an algorithm for transforming an IFDS problem 
into an IDE problem that expresses the feasibility of paths
in light of correlated calls.
Informally speaking, our approach associates with each edge in an
interprocedural CFG a function that records the types of 
variables that are used as the receiver of correlated method calls. Paths that 
are composed of edges in which the same receiver expression has different types
are infeasible, and the propagation of dataflow facts along such paths is
prevented. Applying our technique to an IFDS-based taint analysis would enable
the resulting IDE-based taint analysis to determine that no secret value can flow from
line~\ref{line:Afoo} to the print statement on line~\ref{line:Bbar}.
\mtodo{Maybe emphasize that more generally, the program is not
considered to leak secret information, and not mention the line numbers?}

### 2014-12-12 content/impl.tex
highlight and font

  Returning a secret value in method \verb'A.foo' creates a ``diagonal'' edge from the $\Lambda$-fact to the secret fact $\psi$. 
  The diagonal edge is labeled with the micro function $\lambda m\,.\,\botcc$. Thus, at the end node of the method, every receiver is mapped to the set of all types~$\bot_T$.

On the end-return edge from \verb'A.foo' to \verb'main', the set of types for the receiver \verb'a' is restricted by the micro function $\lambda m\,.\,m[\texttt a\to m(\texttt a)\cap\{\texttt A\}]$ on the edge corresponding to the assignment of the return value $\psi$ to \verb'v'.

Similarly, on the call-start edge from \verb'main' to \verb'B.bar', the possible types
of the receiver \verb'a' are further restricted by the micro-function
$\lambda m\,.\,m[\texttt a\to m(\texttt a)\cap\{\texttt B\}]$.
on the edge that passes the argument \verb'v' to the parameter \verb's'.

The composition of these micro functions results in the empty set as the possible
types of the receiver \verb'a', indicating that this data flow path that would
result in an information leak is actually infeasible.
\end{example}

>>>>

  Returning a secret value in method \code{A.foo} creates a ``diagonal'' edge from the $\Lambda$-fact to the secret fact $\psi$. 
  The diagonal edge is labeled with the micro function $\lambda m\,.\,\botcc$. Thus, at the end node of the method, every receiver is mapped to the set of all types~$\bot_T$.

On the end-return edge from \code{A.foo} to \code{main}, the set of types for the receiver \code{a} is restricted by the micro function $\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code A\}]$ on the edge corresponding to the assignment of the return value $\psi$ to \code v.

Similarly, on the call-start edge from \code{main} to \code{B.bar}, the possible types
of the receiver \code{a} are further restricted by the micro-function
$\lambda m\,.\,m[\code a\to m(\code a)\cap\{\code B\}]$.
on the edge that passes the argument \code{v} to the parameter \code{s}.

The composition of these micro functions results in the empty set as the possible
types of the receiver \code{a}, indicating that this data flow path that would
result in an information leak is actually infeasible.
\end{example}
